|

### 2023-05-03 paper.Rmd
reworked 2.2

Many different hypothesis tests are available to detect specific model defects. For example, the presence of heteroskedasticity can usually be tested by applying the White test [@white1980heteroskedasticity] or the Breusch-Pagan (BP) test [@breusch1979simple], which are both derived from the Lagrange multiplier test [@silvey1959lagrangian] principle that relies on the asymptotic properties of the null distribution. To test specific forms of non-linearity, one may apply the F-test as a model structural test to examine the significance of specific polynomial and non-linear forms of the predictors, or the significance of proxy variables as in the Ramsey Regression Equation Specification Error Test (RESET) [@ramsey1969tests]. The Shapiro-Wilk (SW) normality test [@shapiro1965analysis] is the most widely used test of non-normality included by many of the statistical software programs. The Jarque-Bera test [@jarque1980efficient] is also used to directly check whether the sample skewness and kurtosis match a normal distribution.

@@

We would expect the RESET test for non-linearity to reject residual plot B, the BP test for heteroskedasticity to reject the residual plot C, and the SW test for non-normality to reject residual plot D, which they all do and all tests also correctly fail to reject residual plot A. Interestingly, the BP and SW tests also reject the residual plots exhibiting structure that they weren't designed for. @cook1982residuals explain that most residual-based tests for particular types of departure from model assumptions are also sensitive to other types of departures. This could be considered a Type III error [@kimball1957errors], where the null hypothesis of good residuals is correctly rejected but for the wrong reason. Also, some types of departure can have elements of other types of departure, for example, non-linearity could be viewed as heteroskedasticity. Additionally, other data problems such as outliers can trigger rejection (or not) of the null hypothesis [@cook1999applied].

>>>>

Many different hypothesis tests are available to detect specific model defects. For example, the presence of heteroskedasticity can usually be tested by applying the White test [@white1980heteroskedasticity] or the Breusch-Pagan (BP) test [@breusch1979simple], which are both derived from the Lagrange multiplier test [@silvey1959lagrangian] principle that relies on the asymptotic properties of the null distribution. To test specific forms of non-linearity, one may apply the F-test as a model structural test to examine the significance of a specific polynomial and non-linear forms of the predictors, or the significance of proxy variables as in the Ramsey Regression Equation Specification Error Test (RESET) [@ramsey1969tests]. The Shapiro-Wilk (SW) normality test [@shapiro1965analysis] is the most widely used test of non-normality included by many of the statistical software programs. The Jarque-Bera test [@jarque1980efficient] is also used to directly check whether the sample skewness and kurtosis match a normal distribution.

@@

For residual plots in Figure \ref{fig:residual-plot-common-departures}, we would expect the RESET test for non-linearity to reject residual plot B, the BP test for heteroskedasticity to reject the residual plot C, and the SW test for non-normality to reject residual plot D, which they all do and all tests also correctly fail to reject residual plot A. Interestingly, the BP and SW tests also reject the residual plots exhibiting structure that they weren't designed for. @cook1982residuals explain that most residual-based tests for a particular departure from the model assumptions are also sensitive to other types of departures. This could be considered a Type III error [@kimball1957errors], where the null hypothesis of good residuals is correctly rejected but for the wrong reason. Also, some types of departure can have elements of other types of departure, for example, non-linearity can appear like heteroskedasticity. Additionally, other data problems such as outliers can trigger rejection (or not) of the null hypothesis [@cook1999applied].
